Sample size

### 2021-04-16 scripts/r/sample-size/sample-size.Rmd
:sparkles: - transform OR to z-scores for sample size simulations

```{r Silberzahn}
# load in Silberzahn et al. data: https://osf.io/fa743/
silber <- read_csv("https://osf.io/fa743/download")

@@

# set weakly informative priors
# mean OR
round(mean(silber$OR), 2)

priors <- c(
  prior(normal(1, 1), class = Intercept),
  prior(cauchy(0, 1), class = sd)
)

# run simple model
silber_sd <- brm(
  OR ~ (1 | Team),
  data = silber,
  prior = priors,
  chain = 4,
  iter = 4000,
  cores = 4,
  backend = "cmdstanr", threads = threading(4),
  control = list(adapt_delta = 0.99999, max_treedepth = 15),
  file = "./models/sims/silber_sd"
)

@@

```{r functions}
simulate_data <- function(n, sd) {
  tibble::tibble(
    odds = rnorm(n, 1, sd),
    # no measurement error model for the simulation
    # es_se = rhcauchy(n, 0.15),
    team = letters[1:n]
  )
}

@@

  meta_bm <- brms::brm(
    odds ~
      (1 | team),
    data = data,
    prior = priors,
    chain = 4,
    cores = 4,
    backend = "cmdstanr", threads = brms::threading(4),
    control = list(adapt_delta = 0.9999, max_treedepth = 15),
  )

>>>>

```{r Silberzahn}
# load in Silberzahn et al. data: https://osf.io/fa743/
silber <- read_csv("https://osf.io/fa743/download") %>%
  mutate(
    z_score = log(OR) / ((log(OR) - log(OR_lo)) / 1.96)
  ) %>%
  filter(z_score < 6)

@@

# set weakly informative priors
# mean OR
round(mean(silber$z_score), 2)

priors <- c(
  prior(normal(0, 1), class = Intercept),
  prior(cauchy(0, 1), class = sd)
)

# run simple model
silber_sd <- brm(
  z_score ~ (1 | Team),
  data = silber,
  prior = priors,
  chain = 4,
  iter = 4000,
  cores = 4,
  backend = "cmdstanr", threads = threading(4),
  control = list(adapt_delta = 0.99999, max_treedepth = 15),
  file = "./models/sims/silber_sd"
)

@@

```{r functions}
simulate_data <- function(n, sd) {
  tibble::tibble(
    z_score = rnorm(n, 0, sd),
    # no measurement error model for the simulation
    # es_se = rhcauchy(n, 0.15),
    team = letters[1:n]
  )
}

@@

  meta_bm <- brms::brm(
    z_score ~
      (1 | team),
    data = data,
    prior = priors,
    chain = 4,
    iter = 6000,
    cores = 4,
    backend = "cmdstanr", threads = brms::threading(4),
    control = list(adapt_delta = 0.9999, max_treedepth = 15),
  )
